---
title: "tmp_DMR"
author: "Jakobi Milan"
date: "6 mai 2019"
output: html_document
---

# Genes DMR methylation

To obtain a satisfying view of genes DMRs, we firstly index probes per DMRs and then per genes based on a distance treshold, fixed here at 100k bp, giving a large window allowing the script to catch away DMRs.

```{r}
targeted_genes <- penda_superup_deregulated
features <- get_features(targeted_genes, study = trscr_lusc, up_str = 7500, dwn_str = 7500)

```


```{r}
DMRs100k <- get_indexed_DMRs()
table(sapply(DMRs100k, length))
barplot(table(sapply(DMRs100k, length)))
```


Even with a 100k large window, almost half of our genes do not have DMRs indexed, and 25% have only one, which is a serious problem :
with such a few count of DMRs indexed per genes, it is impossible to distinguish a consistent pattern and to establish relevant hypothesis.

Once the indexing done, we can vizualise, with a `plot_gene_dmr` function :

```{r}
plot_gene_dmr("PKMYT1")
plot_gene_dmr("CDT1")
plot_gene_dmr("ESPL1")

```

The color gradient used is defined by the `breaks` object : from 0 to 0.33, a gradient of cyan is used, from 0.34 to 0.66 is used a black gradient and from 0.66 to 1 is used a red gradient. The function also returns the table of values used to plot the heatmap, giving DMRs names and a more precise overview. Note that the fun used to aggregate values can be chosed, and is `mean` by default.

Yet, i didn't find any obvious patterns of transcription/methylation correlated variations.
