---
title: "Toto"
author: "Titi"
date: "21 mars 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


# Import des données.


```{r echo=FALSE, results ="hide"}
source("~/projects/supergenes/fun_preprocess.R")
source("~/projects/supergenes/fun_plots.R")
print("Loading databases...")

if (!exists("epic")) {
  print("Loading Epic metadata .")
  epic_orig = readRDS("~/projects/supergenes/data/EPIC.hg38.manifest.gencode.v22.rds")
  # epic_orig = readRDS("~/projects/datashare/platforms/EPIC.hg38.manifest.rds")
  epic = as.data.frame(epic_orig)
  rownames(epic) = names(epic_orig)
  head(epic)
  pf_chr_colname = "seqnames"
  pf_pos_colname = "start"
  epic = epic[order(epic[[pf_chr_colname]], epic[[pf_pos_colname]]),]
}



if (!exists("trscr_lusc")) {
  print("Loading LUSC transcription data...")
trscr_lusc = readRDS("~/projects/supergenes/data/tcga_studies/study_TCGA-LUSC_trscr.rds")
}


if (!exists("meth_lusc")) {
  print("Loading LUSC methylation data...")
meth_lusc = readRDS("~/projects/supergenes/data/tcga_studies/study_TCGA-LUSC_meth.rds")
}

if(!exists("penda_superup_deregulated")) {
  print("Loading superexpressed genes database...")
  penda_superup_deregulated = as.data.frame(readxl::read_excel("~/projects/supergenes/data/tables_penda.xlsx"))
  rownames(penda_superup_deregulated) <- penda_superup_deregulated[,1]; penda_superup_deregulated <- penda_superup_deregulated[,-1]
  
  for (i in 1:dim(penda_superup_deregulated)[1]){
    if (is.element(i,c(1:3,178:dim(penda_superup_deregulated)[1])))
      {penda_superup_deregulated[i,1] <- 1}
    else {penda_superup_deregulated[i,1] <- 0}
    
    if (i <= 177)
      {penda_superup_deregulated[i,2] <- 1}
    else {penda_superup_deregulated[i,2] <- 0}
    
  }
}

if(!exists("penda_superdown_deregulated")){
  print("Loading underexpressed genes database...")
  penda_superdown_deregulated = as.data.frame(readxl::read_excel("~/projects/supergenes/data/tables_penda.xlsx",sheet = 2))
  rownames(penda_superdown_deregulated) <- penda_superdown_deregulated[,1]; penda_superdown_deregulated <- penda_superdown_deregulated[,-1]
  
  for (i in 1:dim(penda_superdown_deregulated)[1]){
    if (is.element(i,c(1:123,385:dim(penda_superdown_deregulated)[1]))) 
    {penda_superdown_deregulated[i,1] <- 1}
    else {penda_superdown_deregulated[i,1]<- 0}
    
    if(i <= 384)
    {penda_superdown_deregulated[i,2] <- 1}
    else {penda_superdown_deregulated[i,2]<- 0}
    
  } 
}
  
  
if(!exists("penda_super_conserved")){
  print("Loading conserved genes database...")
  penda_superconserved = as.data.frame(readxl::read_excel("~/projects/supergenes/data/tables_penda.xlsx",sheet = 3))
  rownames(penda_superconserved) <- penda_superconserved[,1]; penda_superconserved <- penda_superconserved[,-1]
    
    for (i in 1:dim(penda_superconserved)[1]){
      if (is.element(i,c(1:33,80:dim(penda_superconserved)[1])))
      {penda_superconserved[i,1] <- 1}
      else {penda_superconserved[i,1] <- 0}
      
      if(i <= 79)
      {penda_superconserved[i,2] <- 1}
      else {penda_superconserved[i,2] <- 0}
    }
  
}

```

- The 







# Data preprocessing



```{r}
features = get_features(penda_superdown_deregulated,index_pathology = 2,trscr_lusc, up_str = 2500, dwn_str = 2500, nb_probe_min = 1)
```


- `r dim(features)[1]` Genes were selected given the parameters. We can now index probes by genes for the ones we selected.
- `r length(unique(unlist(feat_indexed_probes[rownames(sub_features)])))` CpGs 
- corresponding to `r length(rownames(sub_features))` genes given that we excluded genes with less than `r nb_probe_min` in our window of `r paste(up_str,";",dwn_str)` around the transcription starting site (TSS).


```{r}
catalog(features)
```


```{r}
plot_selected_gene("GRK5",expr_data = trscr_lusc$data, meth_data = meth_lusc$data, probes_index = features$probes)
```



```{r}
plot_selected_probes("GRK5",nbins = 6)
```

