---
title: "Binreg Analysis"
author: "Jakobi Milan"
date: "`r Sys.Date()`"
output: 
  rmarkdown::html_document:
    toc: true
    toc_float: true
    toc_depth: 3
    number_sections: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(collapse=TRUE, comment = "#>", fig.width=9, fig.height=6, eval=TRUE, echo=TRUE, results="hide", message=FALSE, warning = FALSE)

source("~/projects/supergenes/src/import_data.R")
```

# Foreword

This vignette is the fourth procuded during my internship in TIMC-IMAG lab (BCM team). It is divided into two parts.
The first one is the visualization of transcription along with heatmap of selected_genes closests DMRs ( window = 100k). The second one offer a new physical gene partition to analyze methylation.

# Updated genes expression profile 

We first divided our genes into 6 bins (-2500,-1500,-500,TSS,+500,+1500,+2500) to overview methylation measures over it. Then, was proposed a second approach by dividing genes into biological regions such as exons, introns etc. The following work flow logically from it : downstream the TSS, the biological regions approach is conserved. Upstream the TSS, the gene is separated into 3 bins : -2500:-1500, -1500:-500 and -500:TSS, to refine our vizualisation.


## Plot per genes

```{r include=FALSE}
targeted_genes <- penda_superup_deregulated
features <- get_features(targeted_genes, study = trscr_lusc, up_str = 7500, dwn_str = 7500)
```


Here are some outputs of a `plot_binreg` function. For clarity, the large source code is not given here and is available on github. The examples plots are the same as used in the DMRs vignette on purpose.

```{r echo=FALSE}
plot_binreg("OTX1")
plot_binreg("MCM2")
plot_binreg("TROAP")
```

As you mate note, the closest region to the TSS is sometimes overlapping with the TSS closest bin. It can lead to index a probe in both. This overlap is on purpose since border_indexs of biological regions can be blurred, i thought it was smarter to risk some noise than determine for good the matter.

# Wide database heatmaps

## Heatmaps superup

We first define a `get_indexed_binreg` indexing probes as shown in previous plots.


We can now repeat our usual pipeline to visualize obtained results. It is noticeable that Rsd heatmap ( relative squared error), defined as $\frac{\sigma}{| \mu |} \in [0,+\infty[$, is not well really informative because of its limits properties which are hard to deal with in a algorithmic way.



### Healthy tissues


```{r}
feat_ind <- get_indexed_binreg()
map_binreg<-reduce_map(feat_ind,c("bin1","bin2","bin3","INTER","UTR5","INTRON","CDS","UTR3"))
means_per_regions_per_genes_per_patient_h<- reduce_rows(meth_normal,map_binreg, mean ,na.rm=T)
means_h <- subset_vals_per_bins(data = meth_normal,
                              values_per_patient = means_per_regions_per_genes_per_patient_h,
                              fun = mean,
                              binlist=c("bin1","bin2","bin3","INTER","UTR5","INTRON","CDS","UTR3"))

meth_heatmap(means_h, main = "mean of means superup/healthy")

```

```{r}
sd_per_regions_per_genes_per_patient_h <- reduce_rows(meth_normal,map_binreg, sd ,na.rm=T)
sds_h <- subset_vals_per_bins(data = meth_normal,
                            values_per_patient = sd_per_regions_per_genes_per_patient_h,
                            fun = sd,
                            binlist=c("bin1","bin2","bin3","INTER","UTR5","INTRON","CDS","UTR3"))
meth_heatmap(sds_h, main = "mean of sd superup/healthy")

```

```{r}
rsd_per_regions_per_genes_per_patient_h <- reduce_rows(meth_normal,map_binreg, rsd ,na.rm=T)
rsds_h <- subset_vals_per_bins(data = meth_normal,
                             values_per_patient = rsd_per_regions_per_genes_per_patient_h,
                             fun = rsd,
                             binlist=c("bin1","bin2","bin3","INTER","UTR5","INTRON","CDS","UTR3"))
meth_heatmap(rsds_h, main = "mean of rsd superup/healthy")
```


### Tumoral tissues

```{r}
means_per_regions_per_genes_per_patient_t <- reduce_rows(meth_tumoral,map_binreg, mean ,na.rm=T)
means_t <- subset_vals_per_bins(data = meth_tumoral,
                             values_per_patient = means_per_regions_per_genes_per_patient_t,
                             fun = mean,
                             binlist=c("bin1","bin2","bin3","INTER","UTR5","INTRON","CDS","UTR3"))

meth_heatmap(means_t, main = "mean of means superup/tumoral")
```


```{r}
sd_per_regions_per_genes_per_patient_t <- reduce_rows(meth_tumoral,map_binreg, sd ,na.rm=T)
sds_t <- subset_vals_per_bins(data = meth_tumoral,
                              values_per_patient = sd_per_regions_per_genes_per_patient_t,
                              fun = sd,
                              binlist=c("bin1","bin2","bin3","INTER","UTR5","INTRON","CDS","UTR3"))
meth_heatmap(sds_t, main = "mean of sd superup/tumoral")
```

```{r}
rsd_per_regions_per_genes_per_patient_t <- reduce_rows(meth_tumoral,map_binreg, rsd ,na.rm=T)
rsds_t <- subset_vals_per_bins(data = meth_tumoral,
                            values_per_patient = rsd_per_regions_per_genes_per_patient_t,
                            fun = rsd,
                            binlist=c("bin1","bin2","bin3","INTER","UTR5","INTRON","CDS","UTR3"))
meth_heatmap(rsds_t, main = "mean of rsd superup/tumoral")
```

### Boxplots

```{r}
boxplot_res(means_h,means_t)
boxplot_res(sds_h,sds_t)
boxplot_res(rsds_h,rsds_t)
```

### Differential values


```{r include=FALSE}
meth_diff <- get_differential_values(meth_tumoral,meth_normal)
```



```{r}
means_per_regions_per_genes_per_patient_d<- reduce_rows(meth_diff,map_binreg, mean ,na.rm=T)
means_d <- subset_vals_per_bins(data = meth_diff,
                              values_per_patient = means_per_regions_per_genes_per_patient_d,
                              fun = mean,
                              binlist=c("bin1","bin2","bin3","INTER","UTR5","INTRON","CDS","UTR3"))

meth_heatmap(means_d, main = "mean of means superup/differential")
```

```{r}
sd_per_regions_per_genes_per_patient_d <- reduce_rows(meth_diff,map_binreg, sd ,na.rm=T)
sds_d <- subset_vals_per_bins(data = meth_diff,
                            values_per_patient = sd_per_regions_per_genes_per_patient_d,
                            fun = sd,
                            binlist=c("bin1","bin2","bin3","INTER","UTR5","INTRON","CDS","UTR3"))
meth_heatmap(sds_d, main = "mean of sd superup/differential")

```

```{r}
rsd_per_regions_per_genes_per_patient_d <- reduce_rows(meth_diff,map_binreg, rsd ,na.rm=T)
rsds_d <- subset_vals_per_bins(data = meth_diff,
                             values_per_patient = rsd_per_regions_per_genes_per_patient_d,
                             fun = rsd,
                             binlist=c("bin1","bin2","bin3","INTER","UTR5","INTRON","CDS","UTR3"))
meth_heatmap(rsds_d, main = "mean of rsd superup/differential")
```


## Heatmaps superdown


```{r include=FALSE}
features_down <- get_features(penda_superdown_deregulated, study = trscr_lusc, up_str = 7500, dwn_str = 7500)
feat_ind_down <- get_indexed_binreg(features_list = features_down)
map_binreg_down<-reduce_map(feat_ind_down,c("bin1","bin2","bin3","INTER","UTR5","INTRON","CDS","UTR3"))
```


### Healthy tissues

```{r echo=FALSE}
means_per_regions_per_genes_per_patient_h_d <- reduce_rows(meth_normal,map_binreg_down, mean ,na.rm=T)
means_h_d <- subset_vals_per_bins(data = meth_normal,
                             values_per_patient = means_per_regions_per_genes_per_patient_h_d,
                             fun = mean,
                             binlist=c("bin1","bin2","bin3","INTER","UTR5","INTRON","CDS","UTR3"),probes_index = feat_ind_down)

meth_heatmap(means_h_d, main = "mean of means superdown/healthy")

```


```{r echo=FALSE}
sd_per_regions_per_genes_per_patient_h_d <- reduce_rows(meth_normal,map_binreg_down, sd ,na.rm=T)
sd_h_d <- subset_vals_per_bins(data = meth_normal,
                             values_per_patient = sd_per_regions_per_genes_per_patient_h_d,
                             fun = sd,
                             binlist=c("bin1","bin2","bin3","INTER","UTR5","INTRON","CDS","UTR3"),probes_index = feat_ind_down)

meth_heatmap(sd_h_d, main = "mean of sd superdown/healthy")
```


```{r echo=FALSE}
rsd_per_regions_per_genes_per_patient_h_d <- reduce_rows(meth_normal,map_binreg_down, sd ,na.rm=T)
rsds_h_d <- subset_vals_per_bins(data = meth_normal,
                             values_per_patient = rsd_per_regions_per_genes_per_patient_h_d,
                             fun = rsd,
                             binlist=c("bin1","bin2","bin3","INTER","UTR5","INTRON","CDS","UTR3"),probes_index = feat_ind_down)

meth_heatmap(rsds_h_d, main = "mean of rsd superdown/healthy")
```

### Tumoral tissues

```{r echo=FALSE}
means_per_regions_per_genes_per_patient_t_d <- reduce_rows(meth_tumoral,map_binreg_down, mean ,na.rm=T)
means_t_d <- subset_vals_per_bins(data = meth_tumoral,
                             values_per_patient = means_per_regions_per_genes_per_patient_t_d,
                             fun = mean,
                             binlist=c("bin1","bin2","bin3","INTER","UTR5","INTRON","CDS","UTR3"),probes_index = feat_ind_down)

meth_heatmap(means_t_d, main = "mean of means superdown/tumoral")

```


```{r echo=FALSE}
sd_per_regions_per_genes_per_patient_t_d <- reduce_rows(meth_tumoral,map_binreg_down, sd ,na.rm=T)
sd_t_d <- subset_vals_per_bins(data = meth_tumoral,
                             values_per_patient = sd_per_regions_per_genes_per_patient_t_d,
                             fun = sd,
                             binlist=c("bin1","bin2","bin3","INTER","UTR5","INTRON","CDS","UTR3"),probes_index = feat_ind_down)

meth_heatmap(sd_t_d, main = "mean of sd superdown/tumoral")
```


```{r echo=FALSE}
rsd_per_regions_per_genes_per_patient_t_d <- reduce_rows(meth_tumoral,map_binreg_down, sd ,na.rm=T)
rsds_t_d <- subset_vals_per_bins(data = meth_tumoral,
                             values_per_patient = rsd_per_regions_per_genes_per_patient_t_d,
                             fun = rsd,
                             binlist=c("bin1","bin2","bin3","INTER","UTR5","INTRON","CDS","UTR3"),probes_index = feat_ind_down)

meth_heatmap(rsds_t_d, main = "mean of rsd superdown/tumoral")
```


### Boxplots

```{r echo=FALSE}
boxplot_res(means_h_d,means_t_d)
boxplot_res(sd_h_d,sd_t_d)
boxplot_res(rsds_h_d,rsds_t_d)
```


### Differential values


```{r echo=FALSE}
means_per_regions_per_genes_per_patient_d_d <- reduce_rows(meth_diff,map_binreg_down, mean ,na.rm=T)
means_d_d <- subset_vals_per_bins(data = meth_diff,
                             values_per_patient = means_per_regions_per_genes_per_patient_d_d,
                             fun = mean,
                             binlist=c("bin1","bin2","bin3","INTER","UTR5","INTRON","CDS","UTR3"),probes_index = feat_ind_down)

meth_heatmap(means_d_d, main = "mean of means superdown/diff")

```


```{r echo=FALSE}
sd_per_regions_per_genes_per_patient_d_d <- reduce_rows(meth_diff,map_binreg_down, sd ,na.rm=T)
sd_d_d <- subset_vals_per_bins(data = meth_diff,
                             values_per_patient = sd_per_regions_per_genes_per_patient_d_d,
                             fun = sd,
                             binlist=c("bin1","bin2","bin3","INTER","UTR5","INTRON","CDS","UTR3"),probes_index = feat_ind_down)

meth_heatmap(sd_d_d, main = "mean of sd superdown/diff")
```


```{r echo=FALSE}
rsd_per_regions_per_genes_per_patient_d_d <- reduce_rows(meth_diff,map_binreg_down, sd ,na.rm=T)
rsds_d_d <- subset_vals_per_bins(data = meth_diff,
                             values_per_patient = rsd_per_regions_per_genes_per_patient_d_d,
                             fun = rsd,
                             binlist=c("bin1","bin2","bin3","INTER","UTR5","INTRON","CDS","UTR3"),probes_index = feat_ind_down)

meth_heatmap(rsds_d_d, main = "mean of rsd superdown/diff")
```



## Heatmap superconserved

```{r include=FALSE}
targeted_genes <- penda_superconserved
features_cons <- get_features(targeted_genes, study = trscr_lusc, up_str = 7500, dwn_str = 7500)
feat_ind_cons <- get_indexed_binreg(features_list = features_cons)
map_binreg_cons<-reduce_map(feat_ind_cons,c("bin1","bin2","bin3","INTER","UTR5","INTRON","CDS","UTR3"))
```



### Healthy tissues


```{r echo=FALSE}
means_per_regions_per_genes_per_patient_h_c <- reduce_rows(meth_normal,map_binreg_cons, mean ,na.rm=T)
means_h_c <- subset_vals_per_bins(data = meth_normal,
                             values_per_patient = means_per_regions_per_genes_per_patient_h_c,
                             fun = mean,
                             binlist=c("bin1","bin2","bin3","INTER","UTR5","INTRON","CDS","UTR3"),probes_index = feat_ind_cons)
meth_heatmap(means_h_c, main = "mean of means supercons/healthy")

```


```{r echo=FALSE}
sd_per_regions_per_genes_per_patient_h_c <- reduce_rows(meth_normal,map_binreg_cons, sd ,na.rm=T)
sd_h_c <- subset_vals_per_bins(data = meth_normal,
                             values_per_patient = sd_per_regions_per_genes_per_patient_h_c,
                             fun = sd,
                             binlist=c("bin1","bin2","bin3","INTER","UTR5","INTRON","CDS","UTR3"),probes_index = feat_ind_cons)

meth_heatmap(sd_h_c, main = "mean of sd supercons/healthy")
```


```{r echo=FALSE}
rsd_per_regions_per_genes_per_patient_h_c <- reduce_rows(meth_normal,map_binreg_cons, sd ,na.rm=T)
rsds_h_c <- subset_vals_per_bins(data = meth_normal,
                             values_per_patient = rsd_per_regions_per_genes_per_patient_h_c,
                             fun = rsd,
                             binlist=c("bin1","bin2","bin3","INTER","UTR5","INTRON","CDS","UTR3"),probes_index = feat_ind_cons)

meth_heatmap(rsds_h_c, main = "mean of rsd supercons/healthy")
```


### Tumoral tissues


```{r echo=FALSE}
means_per_regions_per_genes_per_patient_t_c <- reduce_rows(meth_tumoral,map_binreg_cons, mean ,na.rm=T)
means_t_c <- subset_vals_per_bins(data = meth_tumoral,
                             values_per_patient = means_per_regions_per_genes_per_patient_t_c,
                             fun = mean,
                             binlist=c("bin1","bin2","bin3","INTER","UTR5","INTRON","CDS","UTR3"),probes_index = feat_ind_cons)

meth_heatmap(means_t_c, main = "mean of means supercons/tumoral")

```


```{r echo=FALSE}
sd_per_regions_per_genes_per_patient_t_c <- reduce_rows(meth_tumoral,map_binreg_cons, sd ,na.rm=T)
sd_t_c <- subset_vals_per_bins(data = meth_tumoral,
                             values_per_patient = sd_per_regions_per_genes_per_patient_t_c,
                             fun = sd,
                             binlist=c("bin1","bin2","bin3","INTER","UTR5","INTRON","CDS","UTR3"),probes_index = feat_ind_cons)

meth_heatmap(sd_t_c, main = "mean of sd supercons/tumoral")
```


```{r echo=FALSE}
rsd_per_regions_per_genes_per_patient_t_c <- reduce_rows(meth_tumoral,map_binreg_cons, sd ,na.rm=T)
rsds_t_c <- subset_vals_per_bins(data = meth_tumoral,
                             values_per_patient = rsd_per_regions_per_genes_per_patient_t_c,
                             fun = rsd,
                             binlist=c("bin1","bin2","bin3","INTER","UTR5","INTRON","CDS","UTR3"),probes_index = feat_ind_cons)

meth_heatmap(rsds_t_c, main = "mean of rsd supercons/tumoral")
```


### Boxplots

```{r echo=FALSE}
boxplot_res(means_h_c,means_t_c)
boxplot_res(sd_h_c,sd_t_c)
boxplot_res(rsds_h_c,rsds_t_c)
```

### Differential values

```{r echo=FALSE}
means_per_regions_per_genes_per_patient_d_c <- reduce_rows(meth_diff,map_binreg_cons, mean ,na.rm=T)
means_d_c <- subset_vals_per_bins(data = meth_diff,
                             values_per_patient = means_per_regions_per_genes_per_patient_d_c,
                             fun = mean,
                             binlist=c("bin1","bin2","bin3","INTER","UTR5","INTRON","CDS","UTR3"),probes_index = feat_ind_cons)

meth_heatmap(means_d_c, main = "mean of means supercons/diff")

```


```{r echo=FALSE}
sd_per_regions_per_genes_per_patient_d_c <- reduce_rows(meth_diff,map_binreg_cons, sd ,na.rm=T)
sd_d_c <- subset_vals_per_bins(data = meth_diff,
                             values_per_patient = sd_per_regions_per_genes_per_patient_d_c,
                             fun = sd,
                             binlist=c("bin1","bin2","bin3","INTER","UTR5","INTRON","CDS","UTR3"),probes_index = feat_ind_cons)

meth_heatmap(sd_d_c, main = "mean of sd supercons/diff")
```


```{r echo=FALSE}
rsd_per_regions_per_genes_per_patient_d_c <- reduce_rows(meth_diff,map_binreg_cons, sd ,na.rm=T)
rsds_d_c <- subset_vals_per_bins(data = meth_diff,
                             values_per_patient = rsd_per_regions_per_genes_per_patient_d_c,
                             fun = rsd,
                             binlist=c("bin1","bin2","bin3","INTER","UTR5","INTRON","CDS","UTR3"),probes_index = feat_ind_cons)

meth_heatmap(rsds_d_c, main = "mean of rsd supercons/diff")
```

# Ordered by mean on Intron

## Superup


### Healthy tissues

```{r}
order_index <- order(means_h[,6])
meth_heatmap(means_h, main = "mean of means superup/healthy",order_index=order_index)
meth_heatmap(sds_h, main = "mean of sd superup/healthy", order_index=order_index)
meth_heatmap(rsds_h, main = "mean of rsd superup/healthy",order_index=order_index)
```

### Tumoral tissues

```{r}
meth_heatmap(means_t, main = "mean of means superup/tumoral",order_index=order_index)
meth_heatmap(sds_t, main = "mean of sd superup/tumoral",order_index=order_index)
meth_heatmap(rsds_t, main = "mean of rsd superup/tumoral",order_index=order_index)
```

### Differential

```{r}
meth_heatmap(means_d, main = "mean of means superup/differential",order_index=order_index)
meth_heatmap(sds_d, main = "mean of sd superup/differential",order_index=order_index)
meth_heatmap(rsds_d, main = "mean of rsd superup/differential",order_index=order_index)
```


## Superdown



### Healthy tissues

```{r}
order_index <- order(means_h_d[,6])
meth_heatmap(means_h_d, main = "mean of means superdown/healthy",order_index=order_index)
meth_heatmap(sd_h_d, main = "mean of sd superdown/healthy",order_index=order_index)
meth_heatmap(rsds_h_d, main = "mean of rsd superdown/healthy",order_index=order_index)
```

### Tumoral tissues

```{r}
meth_heatmap(means_t_d, main = "mean of means superdown/tumoral",order_index=order_index)
meth_heatmap(sd_t_d, main = "mean of sd superdown/tumoral",order_index=order_index)
meth_heatmap(rsds_t_d, main = "mean of rsd superdown/tumoral",order_index=order_index)
```

### Differential

```{r}
meth_heatmap(means_d_d, main = "mean of means superdown/diff",order_index=order_index)
meth_heatmap(sd_d_d, main = "mean of sd superdown/diff",order_index=order_index)
meth_heatmap(rsds_d_d, main = "mean of rsd superdown/diff",order_index=order_index)
```


## Supercons


### Healthy tissues

```{r}
order_index <- order(means_h_c[,6])
meth_heatmap(means_h_c, main = "mean of means supercons/healthy",order_index=order_index)
meth_heatmap(sd_h_c, main = "mean of sd supercons/healthy",order_index=order_index)
meth_heatmap(rsds_h_c, main = "mean of rsd supercons/healthy",order_index=order_index)
```

### Tumoral tissues

```{r}
meth_heatmap(means_t_c, main = "mean of means supercons/tumoral",order_index=order_index)
meth_heatmap(sd_t_c, main = "mean of sd supercons/tumoral",order_index=order_index)
meth_heatmap(rsds_t_c, main = "mean of rsd supercons/tumoral",order_index=order_index)
```

### Differential

```{r}
meth_heatmap(means_d_c, main = "mean of means supercons/diff",order_index=order_index)
meth_heatmap(sd_d_c, main = "mean of sd supercons/diff",order_index=order_index)
meth_heatmap(rsds_d_c, main = "mean of rsd supercons/diff",order_index=order_index)
```

# order_indexed by bin3 (closest one to the TSS)

## Superup

### Healthy tissues

```{r}
order_index <- order(means_h[,3])
meth_heatmap(means_h, main = "mean of means superup/healthy",order_index=order_index)
meth_heatmap(sds_h, main = "mean of sd superup/healthy", order_index=order_index)
meth_heatmap(rsds_h, main = "mean of rsd superup/healthy",order_index=order_index)
```

### Tumoral tissues

```{r}
meth_heatmap(means_t, main = "mean of means superup/tumoral",order_index=order_index)
meth_heatmap(sds_t, main = "mean of sd superup/tumoral",order_index=order_index)
meth_heatmap(rsds_t, main = "mean of rsd superup/tumoral",order_index=order_index)
```

### Differential

```{r}
meth_heatmap(means_d, main = "mean of means superup/differential",order_index=order_index)
meth_heatmap(sds_d, main = "mean of sd superup/differential",order_index=order_index)
meth_heatmap(rsds_d, main = "mean of rsd superup/differential",order_index=order_index)
```


## Superdown

### Healthy tissues

```{r}
order_index <- order(means_h_d[,3])
meth_heatmap(means_h_d, main = "mean of means superdown/healthy",order_index=order_index)
meth_heatmap(sd_h_d, main = "mean of sd superdown/healthy",order_index=order_index)
meth_heatmap(rsds_h_d, main = "mean of rsd superdown/healthy",order_index=order_index)
```

### Tumoral tissues

```{r}
meth_heatmap(means_t_d, main = "mean of means superdown/tumoral",order_index=order_index)
meth_heatmap(sd_t_d, main = "mean of sd superdown/tumoral",order_index=order_index)
meth_heatmap(rsds_t_d, main = "mean of rsd superdown/tumoral",order_index=order_index)
```

### Differential

```{r}
meth_heatmap(means_d_d, main = "mean of means superdown/diff",order_index=order_index)
meth_heatmap(sd_d_d, main = "mean of sd superdown/diff",order_index=order_index)
meth_heatmap(rsds_d_d, main = "mean of rsd superdown/diff",order_index=order_index)
```


## Supercons

### Healthy tissues

```{r}
order_index <- order(means_h_c[,3])
meth_heatmap(means_h_c, main = "mean of means supercons/healthy",order_index=order_index)
meth_heatmap(sd_h_c, main = "mean of sd supercons/healthy",order_index=order_index)
meth_heatmap(rsds_h_c, main = "mean of rsd supercons/healthy",order_index=order_index)
```

### Tumoral tissues

```{r}
meth_heatmap(means_t_c, main = "mean of means supercons/tumoral",order_index=order_index)
meth_heatmap(sd_t_c, main = "mean of sd supercons/tumoral",order_index=order_index)
meth_heatmap(rsds_t_c, main = "mean of rsd supercons/tumoral",order_index=order_index)
```

### Differential

```{r}
meth_heatmap(means_d_c, main = "mean of means supercons/diff",order_index=order_index)
meth_heatmap(sd_d_c, main = "mean of sd supercons/diff",order_index=order_index)
meth_heatmap(rsds_d_c, main = "mean of rsd supercons/diff",order_index=order_index)
```














